\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-21 paper/jitp_rr_memo/jitp_rr_memo.tex
added proportion difference figures and discussion

>>>>

	\textbf{Response}: We thank the reviewer for this recommendation. We recognize that the STM results presented in Table 2 conveyed the content, direction of partisan bias, and statistical significance, but did not convey magnitude of differences/effects in any meaningful way. We have added Figure 3, in which we illustrate the magnitudes of the differences between the prevalence of topics based on the mayor's partisanship. We also added discussion of the differences illustrated in this figure. We see this as a major enhancement of our results interpretation.

### 2021-05-21 paper/manuscript_jitp_rr.tex
added proportion difference figures and discussion

>>>>

We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.  To recap these results, the differences in content we find are meaningful both in terms of topics and the sizes of differences based on the partisanship of the city's mayor.

\begin{figure}
\centering
\includegraphics[scale=0.725]{figures/Democratic_topics}\\
\includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites. Depicting topics highlighted in discussion. Top plot gives more Democratic topics, and bottom gives more Republican topics.} \vspace{-.3cm}
\label{fig:demreptop}
\end{figure}
